YouTube Kids: The Effect of YouTube on Children’s Racial Learning

### 2025-04-17 manuscript.qmd
added docx

# Generate table
kable(reliability, 
      align = c("c", "c", "c"),
      # Setting caption here
      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
  kable_styling(position = "center", latex_options = c("striped"))

@@

ggplot(youtube) +
  aes(x = regularity_score, y = malleable_score) +
  facet_wrap(~ gender) +
  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
  geom_point() +
  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
       title = "Attitudes vs. Regularity Scores") +
  my_theme()
```
Finally, turning to the friend choice measure as a gauge of racial attitudes, there were no significant differences between children who chose a friend of the same race/ethnicity as their own and children who did not, in terms of racial attitudes, observations of racial regularities, parasocial relationships with YouTubers, nor choice of favorite YouTuber.

@@

kable(reg_table, align = "lcccc") %>% 
  kable_styling(position = "center", latex_options = c("striped"))

@@

# Print APA-style table
kable(prop_df, align = "c") %>% 
  kable_styling(position = "center", latex_options = c("striped"))

@@

\clearpage
# References
:::{refs}
:::

>>>>

# Generate table
kable(reliability, 
      align = c("c", "c", "c"),
      # Setting caption here
      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") #%>% 
  #kable_styling(position = "center", latex_options = c("striped"))

@@

ggplot(youtube) +
  aes(x = regularity_score, y = malleable_score) +
  facet_wrap(~ gender) +
  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
  geom_point() +
  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
       title = "Attitudes vs. Regularity Scores") +
  my_theme()
```

Finally, turning to the friend choice measure as a gauge of racial attitudes, there were no significant differences between children who chose a friend of the same race/ethnicity as their own and children who did not, in terms of racial attitudes, observations of racial regularities, parasocial relationships with YouTubers, nor choice of favorite YouTuber.

@@

kable(reg_table, align = "lcccc") #%>% 
  #kable_styling(position = "center", latex_options = c("striped"))

@@

# Print APA-style table
kable(prop_df, align = "c") #%>% 
  #kable_styling(position = "center", latex_options = c("striped"))

@@

\clearpage

# References

::: {refs}
:::
